---
title: "Camilo Salazar Hw 6  Math 377"
output:
  pdf_document: default
  html_document: default
---
A study of stress on among the students in a college campus shows that the stress scores follow a Uniform distribution with the lowest stress score equal to 1 and the highest equal to 5. 

Use a sample of 75 students and those four (d,p,q,r) built-in R functions for the probability distribution of random variable to compute the following [Hint: you may use the Central Limit Theorem]:


(a) The probability that the average stress score for the 75 students is less than 2.
```{r}
#(a)
Uniform_distribution <- runif(75,1,5) #scores follow a Uniform distribution
mean_1 <- mean(Uniform_distribution)# the mean found in Uniform_distribution
mean_1
Sd <- sd(Uniform_distribution)#The standard deviation
Sd
p <-pnorm(75, mean_1, Sd)
p<-1-p
p

```

(b) The 90th percentile for the average stress score for the 75 students.
```{r}
#(b)
# remember Mean here is 3 because (a+b)/2 = (1+5)/2 = 3
#sd here is sd = sqrt((b-a)^2/12)
#remeber that the standard devation of the sampling distribution of x bar is sigma_x_bar = sigma/sqrt(n)
qnorm(0.90,3,1.15/sqrt(75))
```
(c) The probability that the total of the 75 stress scores is less than 200.
```{r}
#(c)
#remeber that the standard devation of the sampling distribution of x bar is sigma_x_bar = sigma/sqrt(n)
#The central limit the theorem for sums
#sqrt(n)*sigma of x
n <- 75
sd = sqrt((5-1)^2/12)
standard_Devation_of_sums <-(sqrt(n)*(sd))
standard_Devation_of_sums
# n · µX = the mean of ΣX
mean_ΣX = (75)*3
# the Prob that the score is less than 200 is below
pnorm(200,mean_ΣX,standard_Devation_of_sums)
```
(d) The 90th percentile for the total stress score for the 75 students.
```{r}
#(d)
qnorm(.90,mean_ΣX,standard_Devation_of_sums)
```
PART B:

Consider again the same stress study that is described in PART A and answer the same questions. However, this time assume that the stress score may obtain only the values 1, 2, 3, 4 or 5, with the same probability for obtaining each of the values  [Hint: you may use the Central Limit Theorem] .
```{r}
range_1<-floor(runif(75,1,6))# gives number between 1-5
mean1<-mean(range_1)# there mean 
Standard_devation<-sd(range_1)
prob<-pnorm(75,range_1,mean1)# the prob.
prob<-(1-prob)
prob
```

3. Using the sampling distribution of sample mean to estimate the mean of the variables "xv" and "ys" in the data "scatter1.txt" from the R book.

(a) For the simulation do the sampling 2000 times with sample size n=20 and n=50.
```{r}
#xv
setwd("~/Desktop/R/therbook")
scatter1<-read.table("scatter1.txt",header = TRUE)
attach(scatter1)#guide was from the professor notes lol
str(scatter1)
summary(scatter1)
col<-scatter1$xv
n<-2000 #since n is 2000
X.bar1<-rep(0,n)
for(i in 1:n){
  X.samp<-sample(col,20)
  X.bar1[i]<-mean(X.samp)
  #print(X.bar)
}
hist( X.bar1)
mean(col)
mean(X.bar1)
var(col)#vaneriance 
var(X.bar1)#variance
sd(col)
sd(X.bar1)#standard devation


col<-scatter1$xv
n<-2000 #since n is 2000
X.bar<-rep(0,n)
for(i in 1:n){
  X.samp<-sample(col,50)
  X.bar1[i]<-mean(X.samp)
  #print(X.bar)
}
mean(col)
mean(X.bar)
var(col)
var(X.bar)#variance
sd(col)#standard devation
sd(X.bar)

#ys


col<-scatter1$ys
n<-2000 #since n is 2000
X.bar<-rep(0,n)
for(i in 1:n){
  X.samp<-sample(col,20)
  X.bar[i]<-mean(X.samp)
  #print(X.bar)
}
hist(X.bar)
mean(col)
mean(X.bar)
var(col)#variance
var(X.bar)#variance
sd(col)#standard devation
sd(X.bar)

col<-scatter1$ys
n<-2000 #since n is 2000
X.bar<-rep(0,n)
for(i in 1:n){
  X.samp<-sample(col,50)
  X.bar[i]<-mean(X.samp)
  #print(X.bar)
}
mean(col)
mean(X.bar)
var(col)#variance
var(X.bar)
sd(col)##standard devation
sd(X.bar)
```
(b) Use the sampling distribution(with n=20) that you constructed in (a) to compute an approximation of the probability of the sample mean falling within .5 of the mean of each variable "xv" and "ys". 
```{r}
#(b)
X.bar1<-rep(0,n)
for(i in 1:n){
  X.samp<-sample(col,20)
  X.bar1[i]<-mean(X.samp)
  #print(X.bar)
}
col<-scatter1$xv#set the columns 
col1<-scatter1$ys
setwd("~/Desktop/R/therbook")
data<-read.table("scatter1.txt",header = T)
attach(data)#guide was from the professor notes 
str(data)
summary(data)
#xv
mean(abs(X.bar1-mean(col))<=0.5)

#ys
mean(abs(X.bar1-mean(col1))<=0.5)# fall with in .5
```
(c) Do the same question for (b) with n=50.  
```{r}
#(c)
X.bar2<-rep(0,n)
for(i in 1:n){
  X.samp<-sample(col,50)
  X.bar2[i]<-mean(X.samp)
  #print(X.bar)
}
col<-scatter1$xv#set the columns 
col1<-scatter1$ys
setwd("~/Desktop/R/therbook")
data<-read.table("scatter1.txt",header = T)
attach(data)#guide was from the professor notes 
str(data)
summary(data)
#xv
mean(abs(X.bar2-mean(col))<=0.5)
#mean falling within .5 of the mean 

#ys
mean(abs(X.bar2-mean(col1))<=0.5)
```

4.
A Sampling distribution can be considered in the context of  theoretical distribution models as well.  We can approximate the distribution of the sample mean by simulation:

We do a measurement X from the abstract population distributed by Binomial(10,0.5) . Assume that 70 independent measurements are done with this distribution,(i.e.,the sample size n=70).

(a) Construct the distribution of the sample mean by using a simulation producing 10000 sample means.
```{r}
#(a)
means<-numeric(10000)#from notes 
for (i in 1:10000){
  # n = 70 prob = 0.5 sampling_size= 10 
  means[i]<-mean(rbinom(70,10,.5))
  }
```
(b) Plot the histogram of the distribution that you constructed in (a).
```{r}
#(b)
hist(means,ylim=c(0,3000),main="") 
```
(c) Overlay the smooth density curve of the Normal distribution on the histogram of the sampling distribution that was plotted in (b). 
```{r}
#(c)
hist(means,ylim=c(0,3000),main="") 
mean(means) #means
sd(means) #standard devation 
xv<-seq(4.5,5.5,0.01)#we make a smooth normal curve 
yv <- dnorm(xv,mean=mean(means),sd=sd(means))*1225#From notes
lines(xv,yv)
```
(d) Explain why the variance of the sampling distribution is always smaller than that of the distribution of the population.  
```{r}
#(d)
binomial1<-rbinom(70,10,.5)
mean1<-mean(binomial1)# means
mean1
variance<-var(binomial1)# the variance of rbionm 
variance
aws<-variance/70
aws
```
It is small because the varince I get is 2.311387 and the sampling of the varince I get 0.03301982. Since n = 70 we divide by our varince. Its also becuse we are grouping them.